Analysis for Biracial Grade Retention Project

### 2022-03-30 analysis/analysis.Rmd
Save some output for use in paper

knitreg(map(results_monoracial, convert_marg),
        digits=3, caption="Average marginal differences in probability of being behind grade relative to whites",
        custom.gof.rows=list("State fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Year fixed effects" =   c("No","Yes","Yes","Yes","Yes"),
                             "Grade fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Metro fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Nativity and language" = c("No","No","Yes","Yes","Yes"),
                             "Parent's education" =    c("No","No","No","Yes","Yes"),
                             "Family resources" =      c("No","No","No","No","Yes")))
```

@@

>>>>

knitreg(map(results_monoracial, convert_marg),
        digits=3, caption="Average marginal differences in probability of being behind grade relative to whites",
        custom.gof.rows=list("State fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Year fixed effects" =   c("No","Yes","Yes","Yes","Yes"),
                             "Grade fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Metro fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Nativity and language" = c("No","No","Yes","Yes","Yes"),
                             "Parent's education" =    c("No","No","No","Yes","Yes"),
                             "Family resources" =      c("No","No","No","No","Yes")))

save(results_monoracial, file=here("analysis","output","monoracial_results.RData"))
```

@@

ggplot(coef_table, aes(x=term, y=estimate, color=multiracial,
                       ymin=estimate-1.386*se, ymax=estimate+1.386*se))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=estimate_mid-1.386*se_mid,
                ymax=estimate_mid+1.386*se_mid, fill=multiracial), 
            color=NA, alpha=0.2)+
  geom_linerange(data=subset(coef_table, multiracial))+
  geom_point()+
  coord_flip()+
  facet_grid(mrace~model, scales="free_y")+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank())+
  scale_color_manual(values=c("grey40","red"))+
  scale_fill_manual(values=c("grey40","red"))+
  scale_linetype_manual(values=c(3,1))+
  scale_y_continuous(labels = scales::percent)+
  labs(x=NULL,
       y="average adjusted predicted probability of being behind expected grade")

save(coef_table, file=here("analysis","output","coef_table.RData"))
```
